Combinatorial Proofs and Decomposition Theorems for First-order Logic\vspace{-3ex}

### 2021-01-25 main.tex
up to VIII.B

Let $\Pi$ be a $\FOMLL$ proof of a rectified sequent $\sqn\Gamma$. We now show
how $\Pi$ is translated into a linked fograph
$\fographof\Pi=\tuple{\graphof\Gamma,\linkingof\Pi}$. We proceed
inductively, making a case analysis on the last rule in $\Pi$. At the
same time we are constructing a dualizer $\dsubstof\Pi$, so that in the
end we can conclude that $\fographof\Pi$ is in fact a fonet.
\begin{enumerate}
  %\setlength\itemsep{.5ex}
\item $\Pi$ is $\vlinf{\axr}{}{\sqn{a,\cneg a}}{}$ : Then the only
  link is $\set{a, \dual{a}}$, and $\dsubstof\Pi$ is empty.
\item $\Pi$ is $\vlinf{\ttt}{}{\sqn{\ttt}}{}$ : Then
  $\linkingof\Pi$ and $\dsubstof\Pi$ are both empty.
\item The last rule in $\Pi$ is $\vliinf{\mixr}{}{\sqn{\Gamma',\Gamma''}}{\sqn\Gamma'}{\sqn\Gamma''}$ :
  By induction hypothesis, we have proofs $\Pi'$ and $\Pi''$ of $\Gamma'$ and $\Gamma''$, respectively. We have
  $\graphof{\Gamma}=\graphof{\Gamma'}+\graphof{\Gamma''}$ and let
  $$\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''}
  \qquand
  \dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$$
\item The last rule in $\Pi$ is $\vlinf{\vlor}{}{\sqn{\Gamma_1,A\vlor
    B}}{\sqn{\Gamma_1,A,B}}$ : By induction hypothesis, there is
  proofs $\Pi'$ of $\Gamma'={\Gamma_1,A,B}$. We have
  $\graphof{\Gamma}=\graphof{\Gamma'}$ and let
  $\linkingof\Pi\;=\;\linkingof{\Pi'}$ and
  $\dsubstof\Pi=\dsubstof{\Pi'}$.
\item The last rule in $\Pi$ is $\vliinf{\vlan}{}{\sqn{\Gamma_1,A\vlan
    B, \Gamma_2}}{\sqn{\Gamma_1,A}}{\sqn{B,\Gamma_2}}$ : By induction
  hypothesis, we have proofs $\Pi'$ and $\Pi''$ of
  $\Gamma'=\Gamma_1,A$ and $\Gamma''=B,\Gamma_2$, respectively. We
  have $\graphof{\Gamma}=\graphof{\Gamma_1}+\mbox{$(\graphof A\times\graphof
  B)$}+\graphof{\Gamma_2}$ and we let
  $$\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''} \qquand
  \dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$$
\item The last rule in $\Pi$ is
  $\vlinf{\exists}{}{\sqn{\Gamma_1,\exists x.A}}
  {\sqn{\Gamma_1,A\ssubst{x}{t}}}$ : By induction hypothesis, there is
  a $\Pi'$ of $\Gamma'={\Gamma_1,A\ssubst{x}{t}}$.  For each atom in
  $\Gamma'=\Gamma_1, A \ssubst{x}{t}$, there is a corresponding atom
  in $\Gamma=\Gamma_1, \exists x.A$. We can therefore define the
  linking $\linkingof{\Pi}$ from the linking $\linkingof{\Pi'}$ via
  this correspondence. Then, we let $\dsubstof\Pi$ be
  $\dsubstof{\Pi'}+\ssubst{x}{t}$. Since $\Gamma$ is rectified $x$
  does not yet occur in $\dsubstof{\Pi'}$. Hence $\dsubstof\Pi$ is a
  dualizer of $\fographof\Pi$.
\item The last rule in $\Pi$ is $\vlinf{\forall}{\text{($x$ not free
    in $\Gamma_1$)}}{\sqn{\Gamma_1,\forall x.A}}{\sqn{\Gamma_1,A}}$ :
  By induction hypothesis, there is a proof $\Pi'$ of
  $\Gamma'={\Gamma_1,A}$, which has the same atoms as in
  $\Gamma=\Gamma_1, \forall x.A$.  Hence, we can let
  $\linkingof\Pi\;=\;\linkingof{\Pi'}$ and
  $\dsubstof\Pi=\dsubstof{\Pi'}$. 
\end{enumerate}
%\end{itemize}

\begin{thm}
  \label{thm:MLL1->fonet}
  If $\Pi$ is a $\FOMLL$ proof of a rectified sequent $\sqn\Gamma$,
  then $\fographof\Pi$ is a fonet and $\dsubstof\Pi$ is a dualizer for it.
\end{thm}

@@

A derivation $\Deri$ in $\FOMLS$ is \bfit{rectified} if every line in $\Deri$ is
rectified.

\begin{lemma}
  Let  $\Deri$ be a $\FOMLS$ proof of a formula $A$. Then $\Deri$ is rectified iff $A$ is rectified.
\end{lemma}

\begin{proof}
   The only rules involving bound
   variables are $\forall$ and $\exists$ which both remove a binder (and
   all occurrences of the variable it binds).
\end{proof}

Hence, for a non-rectified  $\FOMLS$ derivation $\Deri$ in $\FOMLS$ we can
define its \bfit{rectification} $\rectif\Deri$ inductively, by rectifying each
line, proceeding step-wise
from conclusion to premise.\footnote{As for formulas,
the rectification of a derivation is unique up to renaming of bound
variables.}

@@

\todo{example here}

\begin{thm}\label{thm:MLS1->fonet}
  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a rectified derivation. Then
  $\fographof\Deri$ is a fonet and $\dsubstof{\Deri}$ a dualizer for it.
\end{thm}

@@

More formally, let $C$ be a formula with $\graphof C=\gC$, to which we
exhaustively apply the following
subformula rewriting steps, to obtain a sequent $\frameof C$:
\begin{enumerate}
\item {\bf Encode dependencies as fresh links.} For each dependency
  $\set{\single {x_i},\single {y_j}}$ in $\gC$, with corresponding
  subformulas $\exists x_i. A$ and $\forall y_j. B$ in $C$, we pick a
  fresh (nullary) predicate symbol $q_{i,j}$, and then replace $\exists
  x_i. A$ by $\dual q_{i,j} \cand \exists x_i. A$, and replace $\forall y_j. B$ by
  $q_{i,j} \cor \forall y_j. B$.
\item {\bf Erase quantifiers.} After step 1, remove all the
  quantifiers, i.e., replace $\exists x_i.A$ by $A$ and replace $\forall
  y_j.B$ by $B$ everywhere.
\item {\bf Simplify atoms.} After step 2, replace every predicate
  $p(t_1 \cdots t_n)$ (resp. $\dual p(t_1 \cdots t_n)$) with a nullary
  predicate symbol $p$ (resp.~$\dual p$)
%% \item {\bf Remove units.} All occurrences of $\ttt$ are replaced by
%%   $q_0\vlor\dual q_0$ and all $\fff$ are replaced by $q_0\vlan\dual
%%   q_0$ for some fresh nullary predicate $q_0$.
\end{enumerate}
The $\linkingof{\frameof C}$ consists of the pairs induced by
$\linkingof\gC$ and the new pairs $\set{q_{i,j},\dual q_{i,j}}$ introduced in
step~1 above.
We call $\frameof C$ the \bfit{frame} of $C$ and we define the \bfit{frame} of $\gC$, denoted
$\frameof\gC$, as
$\tuple{\graphof{\frameof C},\linkingof{\frameof C}}$.

\begin{lemma}\label{lem:frame}
  A linked fograph $\gC$ has an induced bimatching iff its frame $\frameof\gC$ has an induced bimatching.
\end{lemma}

\begin{proof}
  This immediately follows from the construction of the frame.\lutz{is it really an ``iff''? It is easy to construct from a bimatching in $\gC$ a bimatching in the frame. (and I think we only need that direction). But what about the other direction?}
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:MLS1->fonet}]
  From $\Deri$ we construct a derivation $\frameof\Deri$ of $\frameof
  A$ in the propositional fragment of $\FOMLS$, such that
  \hbox{$\fographof{\frameof\Deri}=\frameof{\fographof\Deri}$}.  The
  rules $\aiD,\tttD,\mix$ and $\sw$ are translated trivially, and for
  $\fequ$, it suffices to observe that the frame construction is
  invariant under $\fequ$. Finally, for the rules $\forall$ and
  $\exists$, proceed as follows. Every instance of $\forall$ is
  replaced by the derivation on the right below:\footnote{For better
  readability we omit superfluous parentheses, knowing that we always
  have $\fequ$ incorporating associativity and commutativity of
  $\vlan$ and $\vlor$.}
  \begin{equation*}\small
    \vlinf{\forall}{}{\Scons{\forall y_j.\ttt}}{\Scons{\ttt}}
    %\qquad
    \;\leadsto
    %\qquad
    \vlderivation{
      \vlde{\set{\sw,\fequ}}{\DDeri_2}{\Scons{q_{h_1,j}\vlor\cdots\vlor
          q_{h_j,j}\vlor(\dual q_{h_1,j}\vlan\cdots\vlan\dual
          q_{h_j,j}\vlan\ttt)}}{
        \vlde{\set{\aiD,\tttD}}{\DDeri_1}{
          \Scons{(q_{h_1,j}\vlor \dual q_{h_1,j})\vlan\cdots\vlan(q_{h_j,j}\vlor \dual q_{h_j,j})\vlan\ttt}}{
          \vlhy{\ttt}}}}
  \end{equation*}
  where $h_1,\ldots,h_j$ range over the indices of the existential
  binders dependend on that $y_j$. It is easy to see how $\DDeri_1$ is
  constructed, and for $\DDeri_2$ see,
  e.g. \cite{ESSLI19-notes,gug:str:01,brunnler:tiu:01}\lutz{check if
    it is really there. otherwise \cite{dissvonlutz}} Then, every
  occurrence of $\forall y_j.F$ is replaced by
  $q_{h_1,j}\vlor\cdots\vlor q_{h_j,j}\vlor (\dual
  q_{h_1,j}\vlan\cdots\vlan\dual q_{h_j,j}\vlan F)$ in the derivation
  below that $\forall$-instance. Now, observe that all instances of
  the $\exists$-rule introducing $x_i$ dependend on $y_j$ must occur
  below in the derivation (otherwise $\Deri$ would not be rectified).
  Now consider such an instance $\vlinf{\exists}{}{\Scons{\exists
      x_i.B}}{\Scons{B\ssubst {x_i} t}}$.  Its context $\Sconhole$
  must contain all the $\forall y_j$ the $\exists x_i$ depends on,
  such that $B$ is in their scope. Following the translation of the
  $\forall$ rules above, we can therefore translate the $\exists$-rule
  instance by the following derivation
  \begin{equation*}
    \vlder{\set{\sw,\fequ}}{\DDeri_3}{ S_0\cons{S_1\cons{\cdots
          S_{k_i-1}\cons{S_{k_i}\cons{\dual q_{i,k_1}\vlan\dual
              q_{i,k_2}\vlan\cdots q_{i,k_i}\vlan B'}}\cdots}}}{
      S_0\cons{\dual q_{i,k_1}\vlan S_1\cons{\dual
          q_{i,k_2}\vlan\cdots S_{k_i-1}\cons{\dual q_{i,k_i}\vlan
            S_{k_i}\cons{B'}}\cdots}}}
  \end{equation*}
  where $k_1,\ldots,k_i$ are the indices of of the universal binders
  on which that $x_i$ depends, and $B'$ is $B$ in which all predicates
  are replaced by nullary one (step~3 in the frame construction). The
  derivation $\DDeri_3$ can be constructed in the same way as
  $\DDeri_2$ above.

  Doing this to all instances of the rules $\forall$ and $\exists$ in
  $\Deri$ yields indeed a propositional derivation $\frameof\Deri$
  with
  \hbox{$\fographof{\frameof\Deri}=\frameof{\fographof\Deri}$}. It has
  been shown by Retor\'e~\cite{some tech-report to be found} and
  rediscovered by Stra{\ss}burger~\cite{dissvonlutz} that
  $\fographof{\frameof\Deri}=\tuple{\graphof{\frameof
      C},\linkingof{\frameof\Deri}}$ can not contain an induced
  bimatching. By Lemma~\ref{lem:frame}, $\fographof{\Deri}$ does not
  have an induced bimatching either. Furthemore, it followed from the
  definition of $\dsubstof\Deri$ that it is a dualizer for
  $\fographof{\Deri}$. Hence $\fographof{\Deri}$ is a fonet.
  %% We have
  %% to show that no inference rule in $\FOMLS$ can introduce a
  %% bimatching. For the rules $\forall$, $\aiD$, $\tttD$, $\fequ$, and
  %% $\mix$, this is immediate, as they do not introduce new edges in the
  %% cograph connecting two vertices that are each incident to a leap
  %% edge. The only rules that can do that are $\sw$ and $\exists$. For
  %% the $\sw$-rule, we refer reader to~\cite{retore:???} or
  %% \cite{gug:SIS} or \cite{dissvonlutz} where this property has been
  %% shown in detail. For the rule $\exists$, a potential bimatching can
  %% only be created by a dependency between the \todo{need frame?}
\end{proof}

>>>>

Let $\Pi$ be a $\FOMLL$ proof of a rectified sequent $\sqn\Gamma$ not containing $\fff$. We now show
how $\Pi$ is translated into a linked fograph
$\fographof\Pi=\tuple{\graphof\Gamma,\linkingof\Pi}$. We proceed
inductively, making a case analysis on the last rule in $\Pi$. At the
same time we are constructing a dualizer $\dsubstof\Pi$, so that in the
end we can conclude that $\fographof\Pi$ is in fact a fonet.
\begin{enumerate}
  \addtolength\itemsep{.7ex}
\item $\Pi$ is $\upsmash{\vlinf{\axr}{}{\sqn{a,\cneg a}}{}}$ : Then the only
  link is $\set{a, \dual{a}}$, and $\dsubstof\Pi$ is empty.
\item $\Pi$ is $\smash{\vlinf{\ttt}{}{\sqn{\ttt}}{}}$ : Then
  $\linkingof\Pi$ and $\dsubstof\Pi$ are both empty.
\item The last rule in $\Pi$ is $\vliinf{\mixr}{}{\sqn{\Gamma',\Gamma''}}{\sqn\Gamma'}{\sqn\Gamma''}$ :
  By induction hypothesis, we have proofs $\Pi'$ and $\Pi''$ of $\Gamma'$ and $\Gamma''$, respectively. We have
  $\graphof{\Gamma}=\graphof{\Gamma'}+\graphof{\Gamma''}$ and we can let
  $\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''}$ and
  $\dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$.
\item The last rule in $\Pi$ is $\vlinf{\vlor}{}{\sqn{\Gamma_1,A\vlor
    B}}{\sqn{\Gamma_1,A,B}}$ : By induction hypothesis, there is
  proofs $\Pi'$ of $\Gamma'={\Gamma_1,A,B}$. We have
  $\graphof{\Gamma}=\graphof{\Gamma'}$ and let
  $\linkingof\Pi\;=\;\linkingof{\Pi'}$ and
  $\dsubstof\Pi=\dsubstof{\Pi'}$.
\item The last rule in $\Pi$ is $\vliinf{\vlan}{}{\sqn{\Gamma_1,A\vlan
    B, \Gamma_2}}{\sqn{\Gamma_1,A}}{\sqn{B,\Gamma_2}}$ : By induction
  hypothesis, we have proofs $\Pi'$ and $\Pi''$ of
  $\Gamma'=\Gamma_1,A$ and $\Gamma''=B,\Gamma_2$, respectively. We
  have $\graphof{\Gamma}=\graphof{\Gamma_1}+\mbox{$(\graphof A\times\graphof
  B)$}+\graphof{\Gamma_2}$ and we let
  $\linkingof\Pi\;=\;\linkingof{\Pi'}\cup\linkingof{\Pi''}$ and
  $\dsubstof\Pi=\dsubstof{\Pi'}\cup\dsubstof{\Pi''}$.
\item The last rule in $\Pi$ is
  $\vlinf{\exists}{}{\sqn{\Gamma_1,\exists x.A}}
  {\sqn{\Gamma_1,A\ssubst{x}{t}}}$ : By induction hypothesis, there is
  a $\Pi'$ of $\Gamma'={\Gamma_1,A\ssubst{x}{t}}$.  For each atom in
  $\Gamma'=\Gamma_1, A \ssubst{x}{t}$, there is a corresponding atom
  in $\Gamma=\Gamma_1, \exists x.A$. We can therefore define the
  linking $\linkingof{\Pi}$ from the linking $\linkingof{\Pi'}$ via
  this correspondence. Then, we let $\dsubstof\Pi$ be
  $\dsubstof{\Pi'}+\ssubst{x}{t}$. Since $\Gamma$ is rectified $x$
  does not yet occur in $\dsubstof{\Pi'}$. Hence $\dsubstof\Pi$ is a
  dualizer of $\fographof\Pi$.
\item The last rule in $\Pi$ is $\vlinf{\forall}{\text{($x$ not free
    in $\Gamma_1$)}}{\sqn{\Gamma_1,\forall x.A}}{\sqn{\Gamma_1,A}}$ :
  By induction hypothesis, there is a proof $\Pi'$ of
  $\Gamma'={\Gamma_1,A}$, which has the same atoms as in
  $\Gamma=\Gamma_1, \forall x.A$.  Hence, we can let
  $\linkingof\Pi\;=\;\linkingof{\Pi'}$ and
  $\dsubstof\Pi=\dsubstof{\Pi'}$. 
\end{enumerate}
%\end{itemize}

\begin{thm}
  \label{thm:MLL1->fonet}
  If $\Pi$ is a $\FOMLL$ proof of a rectified $\fff$-free sequent $\sqn\Gamma$,
  then $\fographof\Pi$ is a fonet and $\dsubstof\Pi$ a dualizer for it.
\end{thm}

@@

First observe that in a derivation in $\FOMLS$
where the conclusion is rectified, every line is also rectified, as
the only rules involving bound variables are $\forall$ and $\exists$
which both remove a binder.
Therefore, we can call such a derivation \bfit{rectified}, and
%% if every line in $\Deri$ is
%% rectified.

%% \begin{lemma}
%%   Let  $\Deri$ be a $\FOMLS$ proof of a formula $A$. Then $\Deri$ is rectified iff $A$ is rectified.
%% \end{lemma}

%% \begin{proof}
%%    The only rules involving bound
%%    variables are $\forall$ and $\exists$ which both remove a binder (and
%%    all occurrences of the variable it binds).
%% \end{proof}

%% Hence,
for a non-rectified  $\FOMLS$ derivation $\Deri$ we can
define its \bfit{rectification} $\rectif\Deri$ inductively, by rectifying each
line, proceeding step-wise
from conclusion to premise.\footnote{As for formulas,
the rectification of a derivation is unique up to renaming of bound
variables.}

@@

%\todo{example here}

\begin{thm}\label{thm:MLS1->fonet}
  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be a rectified derivation where $A$ is $\fff$-free. Then
  $\fographof\Deri$ is a fonet and $\dsubstof{\Deri}$ a dualizer for it.
\end{thm}

@@

More formally, let $C$ be a formula with $\graphof C=\gC$, to which we
exhaustively apply the following
subformula rewriting steps, to obtain a sequent $\frameof C$:
\begin{enumerate}
\item {\bf Encode dependencies as fresh links.} For each dependency
  $\set{\single {x_i},\single {y_j}}$ in $\gC$, with corresponding
  subformulas $\exists x_i. A$ and $\forall y_j. B$ in $C$, we pick a
  fresh (nullary) predicate symbol $q_{i,j}$, and then replace $\exists
  x_i. A$ by $\dual q_{i,j} \cand \exists x_i. A$, and replace $\forall y_j. B$ by
  $q_{i,j} \cor \forall y_j. B$.
\item {\bf Erase quantifiers.} After step 1, remove all the
  quantifiers, i.e., replace $\exists x_i.A$ by $A$ and replace $\forall
  y_j.B$ by $B$ everywhere.
\item {\bf Simplify atoms.} After step 2, replace every predicate
  $p(t_1 \cdots t_n)$ (resp. $\dual p(t_1 \cdots t_n)$) with a nullary
  predicate symbol $p$ (resp.~$\dual p$)
%% \item {\bf Remove units.} All occurrences of $\ttt$ are replaced by
%%   $q_0\vlor\dual q_0$ and all $\fff$ are replaced by $q_0\vlan\dual
%%   q_0$ for some fresh nullary predicate $q_0$.
\end{enumerate}
Then $\linkingof{\frameof C}$ consists of the pairs induced by
$\linkingof\gC$ and the new pairs $\set{q_{i,j},\dual q_{i,j}}$ introduced in
step~1 above.
We call $\frameof C$ the \bfit{frame} of $C$ and we define the \bfit{frame} of $\gC$, denoted
$\frameof\gC$, as
$\tuple{\graphof{\frameof C},\linkingof{\frameof C}}$.

\begin{lemma}\label{lem:frame}
  If a linked fograph $\gC$ has an induced bimatching then so does its frame $\frameof\gC$. % has an induced bimatching.
\end{lemma}

\begin{proof}
  Immediately from the construction of the frame.
  %%\lutz{is it really an ``iff''? It is easy to construct from a bimatching in $\gC$ a bimatching in the frame. (and I think we only need that direction). But what about the other direction?}
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:MLS1->fonet}]
  From $\Deri$ we construct a derivation $\frameof\Deri$ of $\frameof
  A$ in the propositional fragment of $\FOMLS$, such that
  \hbox{$\fographof{\frameof\Deri}=\frameof{\fographof\Deri}$}.  The
  rules $\aiD,\tttD,\mix$ and $\sw$ are translated trivially, and for
  $\fequ$, it suffices to observe that the frame construction is
  invariant under $\fequ$. Finally, for the rules $\forall$ and
  $\exists$, proceed as follows. Every instance of $\forall$ is
  replaced by the derivation on the right below:\footnote{For better
  readability we omit superfluous parentheses, knowing that we always
  have $\fequ$ incorporating associativity and commutativity of
  $\vlan$ and $\vlor$.} \vadjust{\vskip-2ex}
  \begin{equation*}
    \scalebox{.95}{$
    \vlinf{\forall}{}{\Scons{\forall y_j.\ttt}}{\Scons{\ttt}}
    %\qquad
    \;\leadsto
    %\qquad
    \vlderivation{
      \vlde{\set{\sw,\fequ}}{\DDeri_2}{\Scons{q_{h_1,j}\vlor\cdots\vlor
          q_{h_j,j}\vlor(\dual q_{h_1,j}\vlan\cdots\vlan\dual
          q_{h_j,j}\vlan\ttt)}}{
        \vlde{\set{\aiD,\tttD}}{\DDeri_1}{
          \Scons{(q_{h_1,j}\vlor \dual q_{h_1,j})\vlan\cdots\vlan(q_{h_j,j}\vlor \dual q_{h_j,j})\vlan\ttt}}{
          \vlhy{\ttt}}}}
    $}
  \end{equation*}
  where $h_1,\ldots,h_j$ range over the indices of the existential
  binders dependend on that $y_j$. It is easy to see how $\DDeri_1$ is
  constructed, and for $\DDeri_2$ see,
  e.g. \cite{ATS:esslli2019,gug:str:01,brunnler:tiu:01,dissvonlutz}. Then, every
  occurrence of $\forall y_j.F$ is replaced by
  $q_{h_1,j}\vlor\cdots\vlor q_{h_j,j}\vlor (\dual
  q_{h_1,j}\vlan\cdots\vlan\dual q_{h_j,j}\vlan F)$ in the derivation
  below that $\forall$-instance. Now, observe that all instances of
  the $\exists$-rule introducing $x_i$ dependend on $y_j$ must occur
  below in the derivation (otherwise $\Deri$ would not be rectified).
  Now consider such an instance $\vlinf{\exists}{}{\Scons{\exists
      x_i.B}}{\Scons{B\ssubst {x_i} t}}$.  Its context $\Sconhole$
  must contain all the $\forall y_j$ the $\exists x_i$ depends on,
  such that $B$ is in their scope. Following the translation of the
  $\forall$ rules above, we can therefore translate the $\exists$-rule
  instance by the following derivation
  \begin{equation*}
    \vlder{\set{\sw,\fequ}}{\DDeri_3}{ S_0\cons{S_1\cons{\cdots
          S_{k_i-1}\cons{S_{k_i}\cons{\dual q_{i,k_1}\vlan\dual
              q_{i,k_2}\vlan\cdots q_{i,k_i}\vlan B'}}\cdots}}}{
      S_0\cons{\dual q_{i,k_1}\vlan S_1\cons{\dual
          q_{i,k_2}\vlan\cdots S_{k_i-1}\cons{\dual q_{i,k_i}\vlan
            S_{k_i}\cons{B'}}\cdots}}}
  \end{equation*}
  where $k_1,\ldots,k_i$ are the indices of of the universal binders
  on which that $x_i$ depends, and $B'$ is $B$ in which all predicates
  are replaced by a nullary one (step~3 in the frame construction). The
  derivation $\DDeri_3$ can be constructed in the same way as
  $\DDeri_2$.

  Doing this to all instances of the rules $\forall$ and $\exists$ in
  $\Deri$ yields indeed a propositional derivation $\frameof\Deri$
  with
  \hbox{$\fographof{\frameof\Deri}=\frameof{\fographof\Deri}$}. It has
  been shown by Retor\'e~\cite{retore:pomset:RR} and
  rediscovered by Stra{\ss}burger~\cite{dissvonlutz} that
  $\fographof{\frameof\Deri}=\tuple{\graphof{\frameof
      C},\linkingof{\frameof\Deri}}$ can not contain an induced
  bimatching. By Lemma~\ref{lem:frame}, $\fographof{\Deri}$ does not
  have an induced bimatching either. Furthemore, it followed from the
  definition of $\dsubstof\Deri$ that it is a dualizer for
  $\fographof{\Deri}$.
  %Hence $\fographof{\Deri}$ is a fonet.
  %% We have
  %% to show that no inference rule in $\FOMLS$ can introduce a
  %% bimatching. For the rules $\forall$, $\aiD$, $\tttD$, $\fequ$, and
  %% $\mix$, this is immediate, as they do not introduce new edges in the
  %% cograph connecting two vertices that are each incident to a leap
  %% edge. The only rules that can do that are $\sw$ and $\exists$. For
  %% the $\sw$-rule, we refer reader to~\cite{retore:???} or
  %% \cite{gug:SIS} or \cite{dissvonlutz} where this property has been
  %% shown in detail. For the rule $\exists$, a potential bimatching can
  %% only be created by a dependency between the \todo{need frame?}
\end{proof}
